Empirical Analysis of Performance Bottlenecks in Graph Neural Network Training with GPUs

### 2020-12-23 NEUROC/sec4-experiments.tex
更新sample size对accuracy的影响.

Since the size of sampled subgraph was much smaller than the original graph, it might affect the accuracy of the trained GNNs.
%
To find out how the batch size affected the accuracy, we trained GNNs under different batch sizes and compared their accuracy with the full-batch training in \figurename~\ref{fig:exp_sampling_relative_batch_size_accuracy}.
%
The experiemental results on other datasets were similar.
%
We used the same hyper-parameters for the sample-based training and the full-batch training.
%
For each dataset and each GNN, we chose the hyper-parameters that achieved the highest accuracy for the full-batch training, according to the experimental results in Section~\ref{sec:effects_of_hyper-parameters_on_performance}.

\begin{figure}[H]
    \centering
    \subfloat[Neighbor sampler on \texttt{amc}]{\includegraphics[height=5cm]{figs/experiments/exp_graphsage_sampling_accuracy_on_amc.pdf}}
    \subfloat[Neighbor sampler on \texttt{fli}]{\includegraphics[height=5cm]{figs/experiments/exp_graphsage_sampling_accuracy_on_fli.pdf}} \\
    \subfloat[Cluster sampler on \texttt{amc}]{\includegraphics[height=5cm]{figs/experiments/exp_cluster_sampling_accuracy_on_amc.pdf}}
    \subfloat[Cluster sampler on \texttt{fli}]{\includegraphics[height=5cm]{figs/experiments/exp_cluster_sampling_accuracy_on_fli.pdf}}
    \caption{Test Accuracy under different batch sizes. FULL means that the full graph participates in the training.}
    \label{fig:exp_sampling_relative_batch_size_accuracy}
\end{figure}

%
With the change of batch size, the accuracy relationship between GNNs is roughly the same.
%
For example, for neigbor sampler, the relationship between GNNs on \texttt{amc} was GCN < GGNN < GAT < GaAN and the relationship on \texttt{amc} was GCN > GGNN > GAT> GaAN.
%
But there was also a little exceptions (cluster sampler on \texttt{amc}, relative batch size was 50\%).
%
To a certain extent, the increase of batch size could bring benefits to all GNNs.
%
However, for different datasets, the accuracy relationship between GNNs was not constant.
%
And this relationship was not related to model complexity.
%
In other words, it was not that the higher the algorithm complexity, the higher the corresponding accuracy.
%
For a specific dataset, in order to obtain high accuracy, the best model could only be selected by constantly trying various models.
%

>>>>

Since the size of sampled subgraph was much smaller than the original graph, it might affect the accuracy of the trained GNNs.
%
To find out how the batch size affected the accuracy, we trained GNNs under different batch sizes and compared their accuracy with the full-batch training in \figurename~\ref{fig:exp_sampling_relative_batch_size_accuracy_graphsage} and \figurename~\ref{fig:exp_sampling_relative_batch_size_accuracy_cluster}.
%
The experiemental results on other datasets were similar.
%
We used the same hyper-parameters for the sample-based training and the full-batch training.
%
For each dataset and each GNN, we chose the hyper-parameters that achieved the highest accuracy for the full-batch training, according to the experimental results in Section~\ref{sec:effects_of_hyper-parameters_on_performance}.

\begin{figure}[H]
    \centering
    \subfloat[\texttt{amp}]{\includegraphics[width=2in]{figs/experiments/exp_graphsage_sampling_accuracy_on_amp.pdf}}
    \subfloat[\texttt{amc}]{\includegraphics[width=2in]{figs/experiments/exp_graphsage_sampling_accuracy_on_amc.pdf}}
    \subfloat[\texttt{fli}]{\includegraphics[width=2in]{figs/experiments/exp_graphsage_sampling_accuracy_on_fli.pdf}}
    \caption{Test accuracy under different batch sizes of the neighbor sampler. FULL means that the full graph participated in the training.}
    \label{fig:exp_sampling_relative_batch_size_accuracy_graphsage}
\end{figure}

\begin{figure}[H]
    \centering
    \subfloat[\texttt{amp}]{\includegraphics[width=2in]{figs/experiments/exp_cluster_sampling_accuracy_on_amp.pdf}}
    \subfloat[\texttt{amc}]{\includegraphics[width=2in]{figs/experiments/exp_cluster_sampling_accuracy_on_amc.pdf}}
    \subfloat[\texttt{fli}]{\includegraphics[width=2in]{figs/experiments/exp_cluster_sampling_accuracy_on_fli.pdf}}
    \caption{Test accuracy under different batch sizes of the cluster sampler. FULL means that the full graph participated in the training.}
    \label{fig:exp_sampling_relative_batch_size_accuracy_cluster}
\end{figure}

The relationship between the batch size and the accuracy was complex.
%
With the change of batch size, the accuracy relationship between GNNs is roughly the same.
%
For example, for neigbor sampler, the relationship between GNNs on \texttt{amc} was GCN < GGNN < GAT < GaAN and the relationship on \texttt{amc} was GCN > GGNN > GAT> GaAN.
%
But there was also a little exceptions (cluster sampler on \texttt{amc}, relative batch size was 50\%).
%
To a certain extent, the increase of batch size could bring benefits to all GNNs.
%
However, for different datasets, the accuracy relationship between GNNs was not constant.
%
And this relationship was not related to model complexity.
%
In other words, it was not that the higher the algorithm complexity, the higher the corresponding accuracy.
%
For a specific dataset, in order to obtain high accuracy, the best model could only be selected by constantly trying various models.
%
